---
title: "Perception example of EZBHDDM"
author: "Adriana F. Chávez De la Peña and Joachim Vandekerckhove"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: true
    highlight: tango
    fig_width: 10 
    fig_height: 5 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rmdformats)
```
# Introduction

Data from [Ratcliff and Rouder (1998)](https://journals.sagepub.com/doi/pdf/10.1111/1467-9280.00067), experiment 1, participant N.H.:

> ''...subjects were asked to decide **whether the overall brightness of pixel arrays displayed on a computer monitor was “high” or “low”** (Fig. 3a). The brightness of a display was controlled by the proportion of the pixels that were white. For each trial, the proportion of white pixels was chosen from one of two distributions, a high distribution or a low distribution, each with fixed mean and standard deviation (Fig. 3b). Feedback was given after each trial to tell the subject whether his or her decision had correctly indicated the distribution...''
>

There are 66 cells in the design following a **two-factor design**:

- **Accuracy vs Speed instructions**: Conditions 1-33 had an accuracy instruction, 34-66 a speed instruction. 

- **More black vs More white pixels**: Conditions 1-16 and 34-49 had more black pixels; conditions 18-33 and 51-66 had more white, and conditions 17 and 50 were ambiguous and will not be used here because they can't provide accuracy measures.

```{r, message=FALSE}
# Load necessary libraries/packages
library(R2jags)
```

# Loading and cleaning the data

### Load the data

```{r}
# Load the data from one participant
data_raw <- read.csv("./nh.tsv", sep = "")
colnames(data_raw) <- c("index","cond","response","RT")
head(data_raw)

# Data set dimensions
dim(data_raw)
```

### Clean the data

```{r}
# Create a copy of the raw data file 
data <- data_raw

# Get 'accuracy' binary coding based on the condition and response in raw data file
accuracy <- as.integer(data_raw$cond > 0  & data_raw$cond < 17 & data_raw$response==1|
                       data_raw$cond > 17 & data_raw$cond < 34 & data_raw$response==2|
                       data_raw$cond > 33 & data_raw$cond < 50 & data_raw$response==1|
                       data_raw$cond > 50 & data_raw$cond < 67 & data_raw$response==2)

# Update the 'response' column of the data copied so it reflects accuracy
data$response <- accuracy

# Remove rows where RT > 3000ms
data <- data[which(data$RT<=3000),]
```

# Get summary statistics

### Write custom function `ez_summaries`

```{r}
# Define a function to compute the summary statistics used by EZ-DDM
ez_summaries <- function(subset){
  # Identify condition ID
  cond <- unique(subset$cond)
  # Return relevant summary statistics
  return(data.frame("nTrials" = nrow(subset),
                    "accRate" = sum(subset$response),
                    "meanRT"  = mean(subset$RT)/1000,
                    "varRT"   = var(subset$RT/1000),
                  # Index variable: Accuracy (-0.5) vs Speed (0.5) condition
                    "Xi"  = as.integer(cond>33)-0.5,
                  # Arbitrary scale of stimulus configuration | 0 is 50/50 black and white 
                    "Xs"  = ((cond-1) %% 33 - 16)/5))
}
```

### Compute summary statistics from data

```{r}
# Initialize an empty output data frame (df)
tmp <- matrix(0,nrow = max(data$cond),ncol = 6)
df <- as.data.frame(tmp)
colnames(df) <- c("nTrials", "sum_accuracy", "mean_rt_correct",
                  "variance_rt_correct", "Xi", "Xs")

# Populate the df output using the ez_summaries function
for(i in 1:max(data$cond)){
  df[i,] <- ez_summaries(data[which(data$cond==i),])
}

# Remove the two ambiguous conditions (17 and 50, 50/50 black and white)
df <- df[-which(df$Xs==0),]
head(df,3)
```

# The model 

The model incorporates an effect ($\beta$) of instruction (i.e., $x_i$, `Xi`) on the *bound parameter ($\alpha$)*. 

\begin{align*}
\alpha &\sim \mbox{Normal}(\mu_\alpha+\beta X_i,\sigma_\alpha)
\end{align*}

We also include a nonlinear regression on the drift rate $\delta$ using instruction (i.e., $x_i$, `Xi`) and stimulus configuration (i.e., $x_s$, `Xs`) as predictors. For the later, we used the absolute value (i.e., $|x_s|$, `abs(Xs)`) to represent the task difficulty getting easier as the black/white balance departs from $50\%$.

\begin{align*}
Y &= \Phi(\beta_1+\beta_2 |X_s|+\beta_3X_i|X_s|)\\
\delta_\mbox{pred} &= \mu_\delta+\beta_0 Y+\beta_4 X_i\\
\delta &\sim \mbox{Normal}(\delta_\mbox{pred},\sigma_\delta)
\end{align*}

In the present example, we focus on the regression parameters capturing the effects of instruction ($\beta_3$, `Beta3`, and $\beta_4$, `Beta4`).


### Write the model in JAGS

EZ JAGS code for the model discussed above:

```{r}
model <- write("
model {
        ##### Priors for hierarchical DDM parameters
        betaweight ~ dnorm(0.00, 1.00)
        beta0 ~ dnorm(0.00, 1.00)
        beta1 ~ dnorm(0.00, 1.00)
        beta2 ~ dnorm(0.00, 1.00)
        beta3 ~ dnorm(0.00, 1.00)
        beta4 ~ dnorm(0.00, 1.00)
        bound_mean ~ dnorm(1.50, (0.20^-2))T( 0.10, 3.00)
        drift_mean ~ dnorm(0.50, (0.50^-2))
        nondt_mean ~ dnorm(0.30, (0.06^-2))T( 0, )
        bound_sdev ~ dunif(0.01, 1.00)
        drift_sdev ~ dunif(0.01, 3.00)
        nondt_sdev ~ dunif(0.01, 0.50)
        
        # Hierarchical distributions of individual DDM parameters.        
        for (p in 1:length(meanRT)) {
            # Here, drift rate is the criterion.
            drift_pred[p] = beta0*phi(beta1 + beta2*abs(Xs[p]) + beta3*Xi[p]*abs(Xs[p])) + beta4 * Xi[p] + drift_mean
            drift[p] ~ dnorm(drift_pred[p], (drift_sdev^-2))
            bound[p] ~ dnorm(bound_mean + betaweight * Xi[p],
                            (bound_sdev^-2))T( 0.10, 3.00)
            nondt[p] ~ dnorm(nondt_mean, (nondt_sdev^-2))
                                            T( 0.05, )
        
            # Forward equations from EZ DDM
            ey[p]  = exp(-bound[p] * drift[p])
            Pc[p]  = 1 / (1 + ey[p])
            PRT[p] = 2 * pow(drift[p], 3) / bound[p] * 
                     pow(ey[p] + 1, 2) / (2 * -bound[p] * 
                     drift[p] * ey[p] - ey[p] * ey[p] + 1)
            MDT[p] = (bound[p] / (2 * drift[p])) * 
                     (1 - ey[p]) / (1 + ey[p])
            MRT[p] = MDT[p] + nondt[p]
        
            # Sampling distributions for summary statistics
            correct[p] ~ dbin(Pc[p], nTrials[p])
            varRT[p]   ~ dnorm(1/PRT[p], 0.5*(correct[p]-1) 
                                         * PRT[p] * PRT[p])
            meanRT[p]  ~ dnorm(MRT[p], PRT[p] * correct[p])
      }
}", "./model_perception.bug")
```


# JAGS


### Specify JAGS setup

```{r}
# General setup
n.chains  <- 4
n.iter    <- 5000
n.burnin  <- 250
n.thin    <- 1

# Pass data to JAGS
data_toJAGS <- list("nTrials"  =  df$nTrials,
                    "meanRT"   =  df$mean_rt_correct,
                    "varRT"    =  df$variance_rt_correct,
                    "correct"  =  df$sum_accuracy,
                    "Xi"   =  df$Xi,
                    "Xs"   =  df$Xs)

# Prepare initial values
myinits <- rep(list(list()), n.chains)
for(i in 1:n.chains){
    myinits[[i]] <- list(drift = rnorm(length(data_toJAGS$nTrials),0,0.1))
}

# Specify parameters to keep track of
parameters <- c('beta3', 'beta4', 'drift', 'drift_pred',
                "Pc", "MRT", "PRT")
```

### Run JAGS

```{r}
samples <- jags(data=data_toJAGS,
                parameters.to.save=parameters,
                model="./model_perception.bug",
                n.chains=n.chains,
                n.iter=n.iter,
                n.burnin=n.burnin,
                n.thin=n.thin,
                DIC=T,
                inits=myinits)
```

### Extract samples

```{r}
# 
drift <- samples$BUGSoutput$sims.list$drift
beta3 <- as.vector(samples$BUGSoutput$sims.list$beta3)
beta4 <- samples$BUGSoutput$sims.list$beta4
drift_pred <- samples$BUGSoutput$sims.list$drift_pred

#
accRate_hat   <- samples$BUGSoutput$sims.list$Pc
rtCorMean_hat <- samples$BUGSoutput$sims.list$MRT
rtCorVar_hat  <- samples$BUGSoutput$sims.list$PRT
```


# Results

```{r}
# Identify conditions to plot on x axis
x_values <- unique(df$Xs)
# Insert a 'jump' in between these values
fit_x <- c(x_values[1:16],NA,x_values[17:32])
```

### Drift rates predicted and recovered

```{r}
#### Extract samples for plotting the nonlinear regression
# Mean drift estimated per condition
means <- apply(drift, 2, mean)
# Get percentiles to later compute error bars around these means
percentiles <- apply(drift,2, quantile, probs=c(0.025,0.975))
lower_percentiles <- percentiles[1,]
upper_percentiles <- percentiles[2,]
# Get mean drift rate predictions (i.e., fitted values)
preds <- apply(drift_pred,2,mean)

# Stack relevant results in a single data frame
results <- data.frame(means,lower_percentiles,upper_percentiles, preds)
# Separate by instruction condition
acc <- results[1:32,]
spd <- results[33:64,]

# Calculate the errors for the error bars
errors_acc <- cbind(acc$means-acc$lower_percentiles, acc$upper_percentiles-acc$means)
errors_spd <- cbind(spd$means-spd$lower_percentiles, spd$upper_percentiles-spd$means)
```

```{r}
### Add a "jump" between conditions for plotting
# Mean drift rates recovered
means_acc <- c(acc$means[1:16],NA,acc$means[17:32])
means_spd <- c(spd$means[1:16],NA,spd$means[17:32])
# Mean predicted drift rates
fit_line_acc <- c(acc$preds[1:16],NA,acc$preds[17:32])
fit_line_spd <- c(spd$preds[1:16],NA,spd$preds[17:32])
# Lower and upper boundaries of the error bars
errors_acc <- cbind(c(acc$lower_percentiles[1:16],NA, acc$lower_percentiles[17:32]),
                    c(acc$upper_percentiles[1:16],NA, acc$upper_percentiles[17:32]))
errors_spd <- cbind(c(spd$lower_percentiles[1:16],NA, spd$lower_percentiles[17:32]),
                    c(spd$upper_percentiles[1:16],NA, spd$upper_percentiles[17:32]))
```

```{r, fig.align='center', out.width="100%"}
par(mfrow = c(1,2), mai=c(0.9,0.6,1,0.3))
line.color  <- "darkorange"
error.color <- "lightblue2"

# Plot for the Accuracy instruction condition
plot(fit_x,fit_line_acc, type="l", lwd=4, col=line.color, ann=F, axes=F,
     ylab="Drift rate", ylim=c(0,6),xaxs = "i", yaxs = "i", xlim=c(-3.5,3.5))
polygon(c(-0.1,0.1,0.1,-0.1),c(0,0,6,6),col = "gray85",
        border = "gray85", lwd = 3, lty = "solid")
polygon(c(-3.5,-0.1,-0.1,-3.5),c(0,0,6,6),col = "gray98",
        border = "gray98", lwd = 3, lty = "solid")
polygon(c(3.5,0.1,0.1,3.5),c(0,0,6,6),col = "gray98",
        border = "gray98", lwd = 3, lty = "solid")
lines(fit_x,fit_line_acc,lwd=4,col=line.color)
arrows(fit_x,errors_acc[,1], fit_x, errors_acc[,2], length=0.05, angle=90, code=3, col=error.color)
points(fit_x, means_acc, col=error.color, pch=16, cex=0.7)
axis(1,c(-2,0,2),c("More black pixels","50/50","More white pixels"), line = 0.1, col.ticks = "white", col="white")
axis(1,c(-4,-2,0,2,4),c("","","","",""), line=0)
axis(2,0:6,0:6, las=2)
mtext("Drift rate", 2, line=2)
mtext("Accuracy instruction", 3, line=1)
mtext("Stimulus configuration", 1, line=3)
box(col="black")

# Plot for the Speed instruction condition
plot(fit_x,fit_line_spd, type="l", lwd=4, col=line.color, ann=F, axes=F,
     ylab="Drift rate", ylim=c(0,6),xaxs = "i", yaxs = "i", xlim=c(-3.5,3.5))
polygon(c(-0.1,0.1,0.1,-0.1),c(0,0,6,6),col = "gray85",
        border = "gray85", lwd = 3, lty = "solid")
polygon(c(-3.5,-0.1,-0.1,-3.5),c(0,0,6,6),col = "gray98",
        border = "gray98", lwd = 3, lty = "solid")
polygon(c(3.5,0.1,0.1,3.5),c(0,0,6,6),col = "gray98",
        border = "gray98", lwd = 3, lty = "solid")
lines(fit_x,fit_line_spd,lwd=4,col=line.color)
arrows(fit_x,errors_spd[,1], fit_x, errors_spd[,2], length=0.05, angle=90, code=3, col=error.color)
points(fit_x, means_spd, col=error.color, pch=16, cex=0.7)
axis(1,c(-2,0,2),c("More black pixels","50/50","More white pixels"), line = 0.1, col.ticks = "white", col="white")
axis(1,c(-4,-2,0,2,4),c("","","","",""), line=0)
axis(2,0:6,0:6, las=2)
mtext("Drift rate", 2, line=2)
mtext("Speed instruction", 3, line=1)
mtext("Stimulus configuration", 1, line=3)
box(col="black")


mtext("Predicted and recovered drift rate per condition",3,outer=TRUE, f=2, line=-2, cex=1.8)
```

### Instruction effect on drift rate slope

```{r}
hist(beta3, freq = FALSE, breaks = 50, col="lightblue3", border = "lightblue3", ann=F, axes = T)
lines(density(beta3), lwd=4, col=line.color)
box(col="black")
mtext("Instruction effect on drift rate slope", cex=1.2, f=2, side=3, line=0.8)
legend("topleft",c("Histogram","KDE"),col=c("lightblue3",line.color),lwd=4, cex=1.1, bty = "n")
mtext("Density",side=2,line=2.15)
mtext("Beta4",side=1,line=2)
#axis(1,seq(0,1.6,0.4),seq(0,1.6,0.4))
#axis(2,seq(0,2,0.5),seq(0,2,0.5),las=2)
```

### Instruction main effect on drift rate

```{r}
hist(beta4, freq = FALSE, breaks = 50, col="lightblue3", border = "lightblue3", ann=F, axes = F,xaxs = "i", yaxs = "i", xlim=c(0,1.6), ylim = c(0,2.2))
lines(density(beta4), lwd=4, col=line.color)
box(col="black")
mtext("Instruction main effect on drift rate", cex=1.2, f=2, side=3, line=0.8)
legend("topleft",c("Histogram","KDE"),col=c("lightblue3",line.color),lwd=4, cex=1.1, bty = "n")
mtext("Density",side=2,line=2.15)
mtext("Beta4",side=1,line=2)
axis(1,seq(0,1.6,0.4),seq(0,1.6,0.4))
axis(2,seq(0,2,0.5),seq(0,2,0.5),las=2)
```


### Model predictions vs data

```{r}
### Prepare JAGS output
est.accRate <- apply(accRate_hat, 2, mean)
est.rtCorMean <- apply(rtCorMean_hat, 2, mean)
est.rtCorVar <- apply(rtCorVar_hat, 2, mean)

# Get percentiles to later compute error bars around these means
percentiles <- apply(accRate_hat,2, quantile, probs=c(0.025,0.975))
lower_percentiles <- percentiles[1,]
upper_percentiles <- percentiles[2,]
```

```{r}
#### Prepare data
# Compute accuracy rate per condition from the summary data
df$acc_rate <- df$sum_accuracy/df$nTrials
# Separate observed data by accuracy/speed condition
df.acc <- df[1:32,]
df.spd <- df[33:64,]

# Concatenate accuracy rates with a 'jump', across speed/accuracy conditions
acc.accRate <- c(df.acc$acc_rate[1:16],NA,df.acc$acc_rate[17:32])
spd.accRate <- c(df.spd$acc_rate[1:16],NA,df.spd$acc_rate[17:32])
# Concatenate mean RT-correct with a 'jump', across speed/accuracy conditions
acc.meanRTcor <- c(df.acc$mean_rt_correct[1:16],NA,df.acc$mean_rt_correct[17:32])
spd.meanRTcor <- c(df.spd$mean_rt_correct[1:16],NA,df.spd$mean_rt_correct[17:32])
```

### Accuracy rate across stimuli configuration levels and instruction conditions

```{r, fig.align='center', out.width="100%"}
par(mfrow = c(1,2), mai=c(0.9,0.6,1,0.3))
plot.color  <- "green3"

# Plot for the Accuracy instructions condition
plot(fit_x,acc.accRate, type="l", lwd=2, col=plot.color, ann=F, axes=F,
     ylim=c(0,1.1),xaxs = "i", yaxs = "i", xlim=c(-3.5,3.5))
polygon(c(-0.1,0.1,0.1,-0.1),c(0,0,1.1,1.1),col = "gray85",
        border = "gray85", lwd = 3, lty = "solid")
polygon(c(-3.5,-0.1,-0.1,-3.5),c(0,0,1.1,1.1),col = "gray98",
        border = "gray98", lwd = 3, lty = "solid")
polygon(c(3.5,0.1,0.1,3.5),c(0,0,1.1,1.1),col = "gray98",
        border = "gray98", lwd = 3, lty = "solid")
lines(fit_x,acc.accRate,lwd=2,col=plot.color)
points(fit_x,acc.accRate,pch=16,col=plot.color)
axis(1,c(-2,0,2),c("More black pixels","50/50","More white pixels"), line = 0.1, col.ticks = "white", col="white")
axis(1,c(-4,-2,0,2,4),c("","","","",""), line=0)
axis(2,seq(0,1,0.2),seq(0,1,0.2), las=2)
mtext("Accuracy rate", 2, line=2.2)
mtext("Accuracy instructions", 3, line=1)
mtext("Stimulus configuration", 1, line=3)
box(col="black")
abline(h=0.5,lty=2, col="gray85")
text(2,0.52,"50% accuracy",col="gray85", cex=0.7)

# Plot for the Speed instructions condition
plot(fit_x,spd.accRate, type="l", lwd=2, col=plot.color, ann=F, axes=F,
     ylim=c(0,1.1),xaxs = "i", yaxs = "i", xlim=c(-3.5,3.5))
polygon(c(-0.1,0.1,0.1,-0.1),c(0,0,1.1,1.1),col = "gray85",
        border = "gray85", lwd = 3, lty = "solid")
polygon(c(-3.5,-0.1,-0.1,-3.5),c(0,0,1.1,1.1),col = "gray98",
        border = "gray98", lwd = 3, lty = "solid")
polygon(c(3.5,0.1,0.1,3.5),c(0,0,1.1,1.1),col = "gray98",
        border = "gray98", lwd = 3, lty = "solid")
lines(fit_x,spd.accRate,lwd=2,col=plot.color)
points(fit_x,spd.accRate,pch=16,col=plot.color)
axis(1,c(-2,0,2),c("More black pixels","50/50","More white pixels"), line = 0.1, col.ticks = "white", col="white")
axis(1,c(-4,-2,0,2,4),c("","","","",""), line=0)
axis(2,seq(0,1,0.2),seq(0,1,0.2), las=2)
mtext("Accuracy rate", 2, line=2.3)
mtext("Speed instructions", 3, line=1)
mtext("Stimulus configuration", 1, line=3)
box(col="black")
abline(h=0.5,lty=2, col="gray85")
text(2,0.52,"50% accuracy",col="gray85", cex=0.7)

mtext("Accuracy rate per condition",3,outer=TRUE, f=2, line=-2, cex=1.8)
```

### Mean correct RT across stimuli configuration levels and instruction conditions

```{r, fig.align='center', out.width="100%"}
par(mfrow = c(1,2), mai=c(0.9,0.6,1,0.3))
plot.color  <- "cyan3"

# Plot for the Accuracy instructions condition
plot(fit_x,acc.meanRTcor, type="l", lwd=2, col=plot.color, ann=F, axes=F,
     ylim=c(0,1),xaxs = "i", yaxs = "i", xlim=c(-3.5,3.5))
polygon(c(-0.1,0.1,0.1,-0.1),c(0,0,1,1),col = "gray85",
        border = "gray85", lwd = 3, lty = "solid")
polygon(c(-3.5,-0.1,-0.1,-3.5),c(0,0,1,1),col = "gray98",
        border = "gray98", lwd = 3, lty = "solid")
polygon(c(3.5,0.1,0.1,3.5),c(0,0,1,1),col = "gray98",
        border = "gray98", lwd = 3, lty = "solid")
lines(fit_x,acc.meanRTcor,lwd=2,col=plot.color)
points(fit_x,acc.meanRTcor,pch=16,col=plot.color)
axis(1,c(-2,0,2),c("More black pixels","50/50","More white pixels"), line = 0.1, col.ticks = "white", col="white")
axis(1,c(-4,-2,0,2,4),c("","","","",""), line=0)
axis(2,seq(0,1,0.2),seq(0,1,0.2), las=2)
mtext("Mean correct RT (secs)", 2, line=2.2)
mtext("Accuracy instruction", 3, line=1)
mtext("Stimulus configuration", 1, line=3)
box(col="black")

# Plot for the Speed instructions condition
plot(fit_x,spd.meanRTcor, type="l", lwd=2, col=plot.color, ann=F, axes=F,
     ylim=c(0,1),xaxs = "i", yaxs = "i", xlim=c(-3.5,3.5))
polygon(c(-0.1,0.1,0.1,-0.1),c(0,0,1,1),col = "gray85",
        border = "gray85", lwd = 3, lty = "solid")
polygon(c(-3.5,-0.1,-0.1,-3.5),c(0,0,1,1),col = "gray98",
        border = "gray98", lwd = 3, lty = "solid")
polygon(c(3.5,0.1,0.1,3.5),c(0,0,1,1),col = "gray98",
        border = "gray98", lwd = 3, lty = "solid")
lines(fit_x,spd.meanRTcor,lwd=4,col=plot.color)
points(fit_x,spd.meanRTcor,pch=16,col=plot.color)
axis(1,c(-2,0,2),c("More black pixels","50/50","More white pixels"), line = 0.1, col.ticks = "white", col="white")
axis(1,c(-4,-2,0,2,4),c("","","","",""), line=0)
axis(2,seq(0,1,0.2),seq(0,1,0.2), las=2)
mtext("Mean correct RT (secs)", 2, line=2.3)
mtext("Speed instruction", 3, line=1)
mtext("Stimulus configuration", 1, line=3)
box(col="black")

mtext("Mean correct RT per condition",3,outer=TRUE, f=2, line=-2, cex=1.8)
```