---
title: "EZBHDDM - Perception example"
author: "Adriana F. Chávez De la Peña and Joachim Vandekerckhove"
date: "`r Sys.Date()`"
output:
  rmdformats::material:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true
    cards: false
    highlight: tango
    fig_width: 12 
    fig_height: 8 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rmdformats)
```
# Introduction

Data from [Ratcliff and Rouder (1998)](https://journals.sagepub.com/doi/pdf/10.1111/1467-9280.00067), experiment 1, participant N.H.:

> ''...subjects were asked to decide **whether the overall brightness of pixel arrays displayed on a computer monitor was “high” or “low”** (Fig. 3a). The brightness of a display was controlled by the proportion of the pixels that were white. For each trial, the proportion of white pixels was chosen from one of two distributions, a high distribution or a low distribution, each with fixed mean and standard deviation (Fig. 3b). Feedback was given after each trial to tell the subject whether his or her decision had correctly indicated the distribution...''
>

There are 66 cells in the design with two main factors:

- **Accuracy vs Speed instructions**: Conditions 1-33 had an accuracy instruction, 34-66 a speed instruction. 

- **More black vs More white pixels**: Conditions 1-16 and 34-49 had more black pixels; conditions 18-33 and 51-66 had more white, and conditions 17 and 50 were ambiguous and will not be used here because they can't provide accuracy measures.

```{r, message=FALSE}
# Load necessary libraries/packages
library(R2jags)
```

# Loading and cleaning the data

### Load the data

```{r}
# Load the data from one participant
data_raw <- read.csv("./nh.tsv", sep = "")
colnames(data_raw) <- c("index","cond","response","RT")
head(data_raw)

# No. of observations
nrow(data_raw)
```

### Clean the data

```{r}
# Create a copy of the raw data file 
data <- data_raw

# Get 'accuracy' binary coding based on the condition and response in raw data file
accuracy <- as.integer(data_raw$cond > 0  & data_raw$cond < 17 & data_raw$response==1|
                       data_raw$cond > 17 & data_raw$cond < 34 & data_raw$response==2|
                       data_raw$cond > 33 & data_raw$cond < 50 & data_raw$response==1|
                       data_raw$cond > 50 & data_raw$cond < 67 & data_raw$response==2)

# Update the 'response' column of the data copied so it reflects accuracy
data$response <- accuracy

# Remove rows where RT > 3000ms
data <- data[which(data$RT<=3000),]
```

# Get summary statistics

**Note:** Since the three-parameters considered by the EZDDM formulation don't predict any difference in shape between the correct and incorrect RT distributions, we use all trials to compute the mean and variance of the RT.

### Write custom function `ez_summaries`

```{r}
# Define a function to compute the summary statistics used by EZ-DDM
ez_summaries <- function(subset){
  # Identify condition ID
  cond <- unique(subset$cond)
  # Return relevant summary statistics
  return(data.frame("nTrials" = nrow(subset),
                    "score" = sum(subset$response),
                    "meanRT"  = mean(subset$RT/1000),
                    "varRT"   = var(subset$RT/1000),
                  # Index variable: Accuracy (-0.5) vs Speed (0.5) condition
                    "Xi"  = as.integer(cond>33)-0.5,
                  # Arbitrary scale of stimulus configuration | 0 is 50/50 black and white 
                    "Xs"  = ((cond-1) %% 33 - 16)/5))
}
```

### Compute summary statistics from data

```{r}
# Initialize an empty output data frame (df)
tmp <- matrix(0,nrow = max(data$cond),ncol = 6)
df <- as.data.frame(tmp)
colnames(df) <- c("nTrials", "sum_accuracy", "mean_rt",
                  "variance_rt", "Xi", "Xs")

# Populate the df output using the ez_summaries function
for(i in 1:max(data$cond)){
  df[i,] <- ez_summaries(data[which(data$cond==i),])
}

# Remove the two ambiguous conditions (17 and 50, with 50/50 black and white)
df <- df[-which(df$Xs==0),]
head(df,3)

# Compute accuracy rate per condition from the summary data
df$acc_rate <- df$sum_accuracy/df$nTrials
```

# The model 

### EZHBDM

The first component of the model is what we called 'the proxy' model: We use the sampling distributions for the three summary statistics computed from the data, (i.e., the number of correct responses $\dot{T}$ and the mean $\dot{M}$ and variance $\dot{V}$ of the response times), which are built from the forward-system of equations in the EZDDM that characterize the proportion of correct responses `PC`, and the mean and precision of the RTs `MRT`, `PRT`.

\begin{align*}
\dot{T} &\sim \mbox{Binomial}(PC,N)\\
\dot{V} &\sim \mbox{Normal}(\frac{1}{PRT},\frac{N-1}{2(PRT)^2})\\
\dot{M} &\sim \mbox{Normal}(MRT, PRT \times N)\\
PC &= \frac{1}{\exp(-\alpha\nu)+1}\\
MRT &= \tau + \frac{\alpha}{2\nu}\frac{\exp(-\alpha\nu)-1}{\exp(-\alpha\nu)+1}\\
PRT &= \frac{\alpha}{2\nu^3}\{\frac{1-2\alpha\nu\exp(-\alpha\nu)-\exp(-\alpha\nu)^2}{(\exp(-\alpha\nu)+1)^2}\}
\end{align*}

### Meta-regression structure

The second component of the model is the meta-regression structure we build to explain the DDM parameters as a function of covariates of interest.

We incorporate an effect ($\beta$) of instruction (i.e., $x_i$, `Xi`) on the *bound parameter ($\alpha$)*. 

\begin{align*}
\alpha &\sim \mbox{Normal}(\mu_\alpha+\beta X_i,\sigma_\alpha)
\end{align*}

We also include a nonlinear regression on the drift rate $\delta$ using instruction (i.e., $x_i$, `Xi`) and stimulus configuration (i.e., $x_s$, `Xs`) as predictors. For the later, we used the absolute value (i.e., $|x_s|$, `abs(Xs)`) to represent the task difficulty getting easier as the black/white balance departs from $50\%$.

\begin{align*}
Z &= \Phi(\beta_1+\beta_2 |X_s|+\beta_3X_i|X_s|)\\
\delta_\mbox{pred} &= \mu_\delta+\beta_0 Z+\beta_4 X_i\\
\delta &\sim \mbox{Normal}(\delta_\mbox{pred},\sigma_\delta)
\end{align*}

In the present example, we focus on the regression parameters capturing the effects of instruction ($\beta_3$, `Beta3`, and $\beta_4$, `Beta4`).


### Write the model in JAGS

```{r}
model <- write("
model {
        ##### Priors for hierarchical DDM parameters
        betaweight ~ dnorm(0.00, 1.00)
        beta0 ~ dnorm(0.00, 1.00)
        beta1 ~ dnorm(0.00, 1.00)
        beta2 ~ dnorm(0.00, 1.00)
        beta3 ~ dnorm(0.00, 1.00)
        beta4 ~ dnorm(0.00, 1.00)
        bound_mean ~ dnorm(1.50, (0.20^-2))T( 0.10, 3.00)
        drift_mean ~ dnorm(0.50, (0.50^-2))
        nondt_mean ~ dnorm(0.30, (0.06^-2))T( 0, )
        bound_sdev ~ dunif(0.01, 1.00)
        drift_sdev ~ dunif(0.01, 3.00)
        nondt_sdev ~ dunif(0.01, 0.50)
        
        # Hierarchical distributions of individual DDM parameters.        
        for (p in 1:length(meanRT)) {
            # Here, we focus on the drift rate
            drift_pred[p] = beta0*phi(beta1 + beta2*abs(Xs[p]) + beta3*Xi[p]*abs(Xs[p])) + beta4 * Xi[p] + drift_mean
            drift[p] ~ dnorm(drift_pred[p], (drift_sdev^-2))
            bound_pred[p] = bound_mean + betaweight * Xi[p]
            bound[p] ~ dnorm(bound_pred[p],(bound_sdev^-2))T( 0.10, 3.00)
            nondt[p] ~ dnorm(nondt_mean, (nondt_sdev^-2))T( 0.05, )
        
            # Forward equations from EZ DDM
            ey[p]  = exp(-bound[p] * drift[p])
            Pc[p]  = 1 / (1 + ey[p])
            PRT[p] = 2 * pow(drift[p], 3) / bound[p] * 
                     pow(ey[p] + 1, 2) / (2 * -bound[p] * 
                     drift[p] * ey[p] - ey[p] * ey[p] + 1)
            MDT[p] = (bound[p] / (2 * drift[p])) * 
                     (1 - ey[p]) / (1 + ey[p])
            MRT[p] = MDT[p] + nondt[p]
            
            # Noiseless predictions from forward EZ DDM
            ey_pred[p]  = exp(-bound_pred[p] * drift_pred[p])
            Pc_pred[p]  = 1 / (1 + ey_pred[p])
            PRT_pred[p] = 2 * pow(drift_pred[p], 3) / bound_pred[p] * 
                     pow(ey_pred[p] + 1, 2) / (2 * -bound_pred[p] * 
                     drift_pred[p] * ey_pred[p] - ey_pred[p] * ey_pred[p] + 1)
            MDT_pred[p] = (bound_pred[p] / (2 * drift_pred[p])) * 
                     (1 - ey_pred[p]) / (1 + ey_pred[p])
            MRT_pred[p] = MDT_pred[p] + nondt_mean
        
            # Sampling distributions for summary statistics
            correct[p] ~ dbin(Pc[p], nTrials[p])
            varRT[p]   ~ dnorm(1/PRT[p], 0.5*(nTrials[p]-1) 
                                         * PRT[p] * PRT[p])
            meanRT[p]  ~ dnorm(MRT[p], PRT[p] * nTrials[p])
      }
}", "./model_perception.bug")
```


# JAGS


### Specify JAGS setup

```{r}
# General setup
n.chains  <- 4;      n.iter    <- 5000
n.burnin  <- 250;    n.thin    <- 1

# Pass data to JAGS
data_toJAGS <- list("nTrials"  =  df$nTrials,
                    "meanRT"   =  df$mean_rt,
                    "varRT"    =  df$variance_rt,
                    "correct"  =  df$sum_accuracy,
                    "Xi"   =  df$Xi, "Xs"   =  df$Xs)

# Prepare initial values
myinits <- rep(list(list()), n.chains)
for(i in 1:n.chains){
    myinits[[i]] <- list(drift = rnorm(length(data_toJAGS$nTrials),0,0.1))
}

# Specify parameters to keep track of
parameters <- c('beta3', 'beta4', 'drift', 'drift_pred',
                "Pc_pred", "MRT_pred", "PRT_pred", "Pc", "PRT", "MRT")
```

### Run JAGS

```{r}
set.seed(127)
samples <- jags(data=data_toJAGS,
                parameters.to.save=parameters,
                model="./model_perception.bug",
                n.chains=n.chains,  n.iter=n.iter,
                n.burnin=n.burnin,  n.thin=n.thin,
                DIC=T, inits=myinits)
```

### Extract posterior samples

```{r}
##### Drift rate parameters
# Recovered drift rates
drift <- samples$BUGSoutput$sims.list$drift
# Effects of instruction
beta3 <- as.vector(samples$BUGSoutput$sims.list$beta3) # Main
beta4 <- samples$BUGSoutput$sims.list$beta4 # Interaction
# Fitted values / Predicted drift rates
drift_pred <- samples$BUGSoutput$sims.list$drift_pred

##### Summary statistics predicted from the predicted drift and boundary
accRate_hat   <- samples$BUGSoutput$sims.list$Pc_pred
rtMean_hat <- samples$BUGSoutput$sims.list$MRT_pred
rtVar_hat  <- 1/samples$BUGSoutput$sims.list$PRT_pred

##### Summary statistics computed from the recovered drift and boundary
Pc   <- samples$BUGSoutput$sims.list$Pc
PRT  <- samples$BUGSoutput$sims.list$PRT
MRT  <- samples$BUGSoutput$sims.list$MRT
```

### Obtain posterior predicted summary statistics

```{r}
# Number of trials per condition
nTrials <- df$nTrials
# Number of posterior samples
n <- nrow(Pc) 
# Number of conditions
J <- ncol(Pc)
# Empty matrices to store posterior predictions
pp_accRate <- matrix(NA, nrow=n, ncol=J)
pp_meanRT  <- matrix(NA, nrow=n, ncol=J)
pp_varRT   <- matrix(NA, nrow=n, ncol=J)
# Obtain posterior predictions using sampling distributions
#        and the summary statistics derived from the recovered
#        drift and boundary parameters
for(i in 1:J){
  correct  <-  rbinom(n,nTrials[i],Pc[,i])
  pp_accRate[,i] <- correct/nTrials[i]
  pp_varRT[,i]   <- rnorm(n,1/PRT[,i], sqrt(2/((nTrials[i]-1) * PRT[,i] * PRT[,i])))
  pp_meanRT[,i]  <- rnorm(n,MRT[,i],sqrt(1/(PRT[,i]*nTrials[i])))
}
```

# Results

## Instruction effect on drift rate slope

```{r, fig.align='center'}
line.color  <- "darkorange"
hist(beta3, freq = FALSE, breaks = 50, col="lightblue3", border = "lightblue3", ann=F, axes = T)
lines(density(beta3), lwd=4, col=line.color)
legend("topleft",c("Histogram","KDE"),col=c("lightblue3",line.color),lwd=4, cex=1.1, bty = "n")
mtext("Instruction effect on drift rate slope", cex=1.2, f=2, side=3, line=0.8)
mtext("Density",side=2,line=2.15)
mtext("Beta 3",side=1,line=2)
box(col="black")
```

## Instruction main effect on drift rate

```{r, fig.align='center'}
hist(beta4, freq = FALSE, breaks = 50, col="lightblue3", border = "lightblue3", ann=F, axes = T,xaxs = "i", yaxs = "i", xlim=c(0,1.6), ylim = c(0,2.2))
lines(density(beta4), lwd=4, col=line.color)
legend("topleft",c("Histogram","KDE"),col=c("lightblue3",line.color),lwd=4, cex=1.1, bty = "n")
mtext("Instruction main effect on drift rate", cex=1.2, f=2, side=3, line=0.8)
mtext("Density",side=2,line=2.15)
mtext("Beta 4",side=1,line=2)
box(col="black")
```

```{r}
# Identify conditions to plot on x axis
x_values <- unique(df$Xs)
# Insert a 'jump' in between these values
fit_x <- c(x_values[1:16],NA,x_values[17:32])
full_x <- c(fit_x,NA,fit_x+6.8)
```

## Drift rates predicted and recovered

```{r}
#### Get mean posterior estimates and percentiles for plotting
# Drift recovered
means <- apply(drift, 2, mean)
percentiles <- apply(drift,2, quantile, probs=c(0.025,0.975))
lower_percentiles <- percentiles[1,]  #  2.5%
upper_percentiles <- percentiles[2,]  # 97.5%
# Drift predictions (i.e., fitted values)
preds <- apply(drift_pred,2,mean)
```

```{r, echo=FALSE, fig.align='center', out.width="100%"}
acc.bckg <- "#FCF2FF"
spd.bckg <- "#F5FAF9"

### Concatenate values by instruction and add a "jump" between pixel condition
makeLines <- function(posterior_object){
  x <- posterior_object
  line_acc <- c(x[1:16], NA,x[17:32])
  line_spd <- c(x[33:48],NA,x[49:64])
  full_line <- c(line_acc, NA, line_spd)
return(full_line)
}

means <- makeLines(means)
fit_line <- makeLines(preds)

# Lower and upper boundaries of the error bars
errors_acc <- cbind(c(lower_percentiles[1:16], NA, lower_percentiles[17:32]),
                    c(upper_percentiles[1:16], NA, upper_percentiles[17:32]))
errors_spd <- cbind(c(lower_percentiles[33:48],NA, lower_percentiles[49:64]),
                    c(upper_percentiles[33:48],NA, upper_percentiles[49:64]))
errors <- rbind(errors_acc,c(NA,NA),errors_spd)

par(pty="m", mfrow = c(1,1), mai=c(1.1,0.6,0.5,0), oma= c(0,0,0,0))
predicted.color  <- "#FF8B0F"
recovered.color <- "#83460A"
point.size <- 1

plot(full_x,fit_line, type="l", lwd=4, col=predicted.color, ann=F, axes=F,
     ylab="Drift rate", ylim=c(0,6),xaxs = "i", yaxs = "i", xlim=c(-3.5,10.3))
# Gray background
polygon(c(-3.5,3.5,3.5,-3.5),c(0,0,6,6),col = acc.bckg, border = "gray98", lwd = 3, lty = "solid")
polygon(c(3.5,10.3,10.3,3.5),c(0,0,6,6),col = spd.bckg, border = "gray98", lwd = 3, lty = "solid")
polygon(c(-0.04,0.04,0.04,-0.04),c(0,0,6,6),col = "gray85", border = "gray85", lwd = 3, lty = "solid")
polygon(c(6.76,6.84,6.84,6.76),c(0,0,6,6),col = "gray85", border = "gray85", lwd = 3, lty = "solid")
lines(full_x,fit_line,lwd=4,col=predicted.color)
arrows(full_x,errors[,1], full_x, errors[,2], length=0.05, angle=90, code=3, col=recovered.color)
points(full_x, means, col=recovered.color, pch=16, cex=point.size)
axis(1,c(-2,0,2,5,7,9),rep(c("More black","50/50","More white"),2), line = 0)
axis(1,c(-4,10.3),c("",""), line = 0, col.ticks = "white")
axis(2,0:6,0:6, las=2)
mtext("Drift rate", 2, line=2)
text(-2,0.35,"Accuracy", cex=1.5)
mtext("Stimulus configuration", 1, line=3)
text(9,0.35,"Speed", cex=1.5)
mtext("Predicted and recovered drift rate per condition",3,outer=TRUE, f=2, line=-1.5, cex=1.8)
```


## Summary statistics derived from the predicted drift rate and boundary

```{r}
## Get mean posteriors
est.accRate   <- apply(accRate_hat, 2, mean)
est.rtMean <- apply(rtMean_hat, 2, mean)
est.rtVar  <- apply(rtVar_hat, 2, mean)
## Get percentiles
perc.accRate   <- apply(accRate_hat,2, quantile, probs=c(0.025,0.975))
perc.rtMean <- apply(rtMean_hat,2, quantile, probs=c(0.025,0.975))
perc.rtVar  <- apply(rtVar_hat,2, quantile, probs=c(0.025,0.975))
```

```{r, echo=FALSE}
## Concatenate per instruction condition, with a "jump" between pixel condition
accRate <- makeLines(df$acc_rate)
meanRT  <- makeLines(df$mean_rt)
varRT   <- makeLines(df$variance_rt)

est.accRate.Full   <- makeLines(est.accRate)
est.rtMean.Full <- makeLines(est.rtMean)
est.rtVar.Full  <- makeLines(est.rtVar)


## Arrange lower and upper percentiles such that we can use polygon() to draw them
# Accuracy rate
err.accRate.acc  <- c(perc.accRate[1,1:16],  perc.accRate[2,16:1],
                      perc.accRate[1,17:32], perc.accRate[2,32:17])
err.accRate.spd  <- c(perc.accRate[1,33:48], perc.accRate[2,48:33],
                      perc.accRate[1,49:64], perc.accRate[2,64:49])
# Mean RT-correct
err.rtMean.acc  <- c(perc.rtMean[1,1:16],  perc.rtMean[2,16:1],
                        perc.rtMean[1,17:32], perc.rtMean[2,32:17])
err.rtMean.spd  <- c(perc.rtMean[1,33:48], perc.rtMean[2,48:33], 
                        perc.rtMean[1,49:64], perc.rtMean[2,64:49])
# RT-correct Variance
err.rtVar.acc  <- c(perc.rtVar[1,1:16],  perc.rtVar[2,16:1],
                       perc.rtVar[1,17:32], perc.rtVar[2,32:17])
err.rtVar.spd  <- c(perc.rtVar[1,33:48], perc.rtVar[2,48:33],
                       perc.rtVar[1,49:64], perc.rtVar[2,64:49])
```

```{r, fig.align='center', out.width="100%", echo=FALSE}
par(pty="m", mfrow = c(1,1), mai=c(1.1,0.6,0.5,0), oma= c(0,0,0,0))
data.color  <- "black"
point.size <- 0.9
error.color <- "#E69FF8"
pred.color <- "#BE07C1"

predAccuracy_plot <- function(accRate, est.accRate.Full, err.accRate.acc, err.accRate.spd){
    plot(full_x,est.accRate.Full, col="white", ann=F, axes=F, 
         ylim=c(0.45,1.05),xaxs = "i", yaxs = "i", xlim=c(-3.5,10.3))
    polygon(c(-3.5,3.5,3.5,-3.5),c(0,0,6,6),col = acc.bckg, border = "gray98", lwd = 3, lty = "solid")
    polygon(c(3.5,10.3,10.3,3.5),c(0,0,6,6),col = spd.bckg, border = "gray98", lwd = 3, lty = "solid")
    polygon(c(-0.04,0.04,0.04,-0.04),c(0,0,6,6),col = "gray85", border = "gray85", lwd = 3, lty = "solid")
    polygon(c(6.76,6.84,6.84,6.76),c(0,0,6,6),col = "gray85", border = "gray85", lwd = 3, lty = "solid")
    polygon(c(full_x[1:16],full_x[16:1]),err.accRate.acc[1:32],col = error.color, border = NA, lwd = 3, lty = "solid")
    polygon(c(full_x[18:33],full_x[33:18]),err.accRate.acc[33:64],col = error.color, border = NA, lwd = 3, lty = "solid")
    polygon(c(full_x[35:50],full_x[50:35]),err.accRate.spd[1:32],col = error.color, border = NA, lwd = 3, lty = "solid")
    polygon(c(full_x[52:67],full_x[67:52]),err.accRate.spd[33:64],col = error.color, border = NA, lwd = 3, lty = "solid")
    lines(full_x,est.accRate.Full,col=pred.color, lwd=3)
    points(full_x,accRate,pch=8,col=data.color, cex=0.7)
    axis(1,c(-2,0,2,5,7,9),rep(c("More black","50/50","More white"),2), line = 0)
    axis(1,c(-4,10.3),c("",""), line = 0, col.ticks = "white")
    axis(2,seq(0,1,0.1),seq(0,1,0.1), las=2)
    text(2.5, 0.47, "Accuracy")
    text(4.2, 0.47, "Speed")
    mtext("Stimulus configuration", 1, line=3)
    abline(h=0.5,lty=2, col="gray50")
    text(9,0.52,"50% accuracy",col="gray50", cex=0.7)
    mtext("Accuracy rate per condition",3,outer=TRUE, f=2, line=-1.5, cex=1.8)
}

predAccuracy_plot(accRate, est.accRate.Full, err.accRate.acc, err.accRate.spd)
```

```{r, fig.align='center', out.width="100%", echo=FALSE}
par(pty="m", mfrow = c(1,1), mai=c(1.1,0.6,0.5,0), oma= c(0,0,0,0))
error.color <- "#6DFA9C"
pred.color <- "#00A437"
point.size <- 0.9

predMeanRT_plot <- function(est.rtMean.Full, meanRT, err.rtMean.acc, err.rtMean.spd){
    plot(full_x,est.rtMean.Full, col="white", ann=F, axes=F, ylim=c(0.2,1), 
         xaxs = "i", yaxs = "i", xlim=c(-3.5,10.3))
    polygon(c(-3.5,3.5,3.5,-3.5),c(0,0,6,6),col = acc.bckg, border = "gray98", lwd = 3, lty = "solid")
    polygon(c(3.5,10.3,10.3,3.5),c(0,0,6,6),col = spd.bckg, border = "gray98", lwd = 3, lty = "solid")
    polygon(c(-0.04,0.04,0.04,-0.04),c(0,0,6,6),col = "gray85", border = "gray85", lwd = 3, lty = "solid")
    polygon(c(6.76,6.84,6.84,6.76),c(0,0,6,6),col = "gray85", border = "gray85", lwd = 3, lty = "solid")
    polygon(c(full_x[1:16],full_x[16:1]),err.rtMean.acc[1:32],col = error.color,
            border = NA, lwd = 3, lty = "solid")
    polygon(c(full_x[18:33],full_x[33:18]),err.rtMean.acc[33:64],col = error.color,
            border = NA, lwd = 3, lty = "solid")
    polygon(c(full_x[35:50],full_x[50:35]),err.rtMean.spd[1:32],col = error.color,
            border = NA, lwd = 3, lty = "solid")
    polygon(c(full_x[52:67],full_x[67:52]),err.rtMean.spd[33:64],col = error.color,
            border = NA, lwd = 3, lty = "solid")
    lines(full_x,est.rtMean.Full,col=pred.color, lwd=3)
    points(full_x,meanRT,pch=8,col=data.color, cex=0.7)
    axis(1,c(-2,0,2,5,7,9),rep(c("More black","50/50","More white"),2), line = 0)
    axis(1,c(-4,10.3),c("",""), line = 0, col.ticks = "white")
    axis(2,seq(0,1,0.1),seq(0,1,0.1), las=2)
    mtext("Mean RT (secs)", 2, line=2.2)
    mtext("Stimulus configuration", 1, line=3)
    text(2.5, 0.95, "Accuracy")
    text(4.2, 0.95, "Speed")
    mtext("Mean RT per condition",3,outer=TRUE, f=2, line=-1.5, cex=1.8)
}

predMeanRT_plot(est.rtMean.Full, meanRT, err.rtMean.acc, err.rtMean.spd)
```

```{r, fig.align='center', out.width="100%", echo=FALSE}
par(pty="m", mfrow = c(1,1), mai=c(1.1,0.6,0.5,0), oma= c(0,0,0,0))
error.color <- "#8CE0FF"
pred.color <- "#095B79"

predVarRT_plot <- function(varRT, est.rtVar.Full, err.rtVar.acc, err.rtVar.spd){
    plot(full_x,est.rtVar.Full, col="white", ann=F, axes=F, ylim=c(0,0.4),
         xaxs = "i", yaxs = "i", xlim=c(-3.5,10.3))
    polygon(c(-3.5,3.5,3.5,-3.5),c(0,0,6,6),col = acc.bckg, border = "gray98", lwd = 3, lty = "solid")
    polygon(c(3.5,10.3,10.3,3.5),c(0,0,6,6),col = spd.bckg, border = "gray98", lwd = 3, lty = "solid")
    polygon(c(-0.04,0.04,0.04,-0.04),c(0,0,6,6),col = "gray85", border = "gray85", lwd = 3, lty = "solid")
    polygon(c(6.76,6.84,6.84,6.76),c(0,0,6,6),col = "gray85", border = "gray85", lwd = 3, lty = "solid")
    polygon(c(full_x[1:16],full_x[16:1]),err.rtVar.acc[1:32],col = error.color,
            border = NA, lwd = 3, lty = "solid")
    polygon(c(full_x[18:33],full_x[33:18]),err.rtVar.acc[33:64],col = error.color,
            border = NA, lwd = 3, lty = "solid")
    polygon(c(full_x[35:50],full_x[50:35]),err.rtVar.spd[1:32],col = error.color,
            border = NA, lwd = 3, lty = "solid")
    polygon(c(full_x[52:67],full_x[67:52]),err.rtVar.spd[33:64],col = error.color,
            border = NA, lwd = 3, lty = "solid")
    lines(full_x,est.rtVar.Full,col=pred.color, lwd=3)
    points(full_x,varRT,pch=8,col=data.color, cex=0.7)
    axis(1,c(-2,0,2,5,7,9),rep(c("More black","50/50","More white"),2), line = 0)
    axis(1,c(-4,10.3),c("",""), line = 0, col.ticks = "white")
    axis(2,seq(0,1,0.1),seq(0,1,0.1), las=2)
    mtext("RT variance", 2, line=2.2)
    text(2.5, 0.37, "Accuracy")
    text(4.2, 0.37, "Speed")
    mtext("Stimulus configuration", 1, line=3)
    mtext("RT Variance per condition",3,outer=TRUE, f=2, line=-1.5, cex=1.8)
}

predVarRT_plot(varRT, est.rtVar.Full, err.rtVar.acc, err.rtVar.spd)
```

## Posterior predictive checks

```{r}
## Get mean posteriors and key percentiles
# Accuracy rate
pp.accRate <- apply(pp_accRate, 2, mean)
pp.perc.accRate <- apply(pp_accRate,2, quantile, probs=c(0.025,0.975))
# Mean RT-correct
pp.rtMean <- apply(pp_meanRT, 2, mean)
pp.perc.rtMean <- apply(pp_meanRT,2, quantile, probs=c(0.025,0.975))
# RT-correct Variance
pp.rtVar <- apply(pp_varRT, 2, mean)
pp.perc.rtVar <- apply(pp_varRT,2, quantile, probs=c(0.025,0.975))
```

```{r, echo=FALSE}
## Concatenate per instruction condition, with a "jump" between pixel condition
est.accRate.Full   <- makeLines(pp.accRate)
est.rtMean.Full <- makeLines(pp.rtMean)
est.rtVar.Full  <- makeLines(pp.rtVar)


## Arrange lower and upper percentiles such that we can use polygon() to draw them
# Accuracy rate
err.accRate.acc  <- c(pp.perc.accRate[1,1:16],  pp.perc.accRate[2,16:1],
                      pp.perc.accRate[1,17:32], pp.perc.accRate[2,32:17])
err.accRate.spd  <- c(pp.perc.accRate[1,33:48], pp.perc.accRate[2,48:33],
                      pp.perc.accRate[1,49:64], pp.perc.accRate[2,64:49])
# Mean RT-correct
err.rtMean.acc  <- c(pp.perc.rtMean[1,1:16],  pp.perc.rtMean[2,16:1],
                        pp.perc.rtMean[1,17:32], pp.perc.rtMean[2,32:17])
err.rtMean.spd  <- c(pp.perc.rtMean[1,33:48], pp.perc.rtMean[2,48:33], 
                        pp.perc.rtMean[1,49:64], pp.perc.rtMean[2,64:49])
# RT-correct Variance
err.rtVar.acc  <- c(pp.perc.rtVar[1,1:16],  pp.perc.rtVar[2,16:1],
                       pp.perc.rtVar[1,17:32], pp.perc.rtVar[2,32:17])
err.rtVar.spd  <- c(pp.perc.rtVar[1,33:48], pp.perc.rtVar[2,48:33],
                       pp.perc.rtVar[1,49:64], pp.perc.rtVar[2,64:49])
```

```{r, fig.align='center', out.width="100%", echo=FALSE}
par(pty="m", mfrow = c(1,1), mai=c(1.1,0.6,0.5,0), oma= c(0,0,0,0))
data.color  <- "black"
point.size <- 0.9
error.color <- "#E69FF8"
pred.color <- "#BE07C1"

predAccuracy_plot(accRate, est.accRate.Full, err.accRate.acc, err.accRate.spd)
```

```{r, fig.align='center', out.width="100%", echo=FALSE}
par(pty="m", mfrow = c(1,1), mai=c(1.1,0.6,0.5,0), oma= c(0,0,0,0))
error.color <- "#6DFA9C"
pred.color <- "#00A437"
point.size <- 0.9

predMeanRT_plot(est.rtMean.Full, meanRT, err.rtMean.acc, err.rtMean.spd)
```

```{r, fig.align='center', out.width="100%", echo=FALSE}
par(pty="m", mfrow = c(1,1), mai=c(1.1,0.6,0.5,0), oma= c(0,0,0,0))
error.color <- "#8CE0FF"
pred.color <- "#095B79"


predVarRT_plot(varRT, est.rtVar.Full, err.rtVar.acc, err.rtVar.spd)
```

